\bf Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-02-05 short/Feb_rewrite/Introduction_to_adaptation_of_chumbley.tex
intro

<!-- \tableofcontents -->

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  error = FALSE, 
  collapse = TRUE,
  comment = "",
  fig.height = 6,
  fig.width = 6,
  fig.align = "center",
  out.width= '\\textwidth',
  cache = FALSE,
  fig.path='figures/',
  echo=FALSE,
  cache=TRUE
)
options(knitr.table.format = "latex")
library(tidyverse)
```
# Introduction

@@

```{r, results='asis'}
library(knitr)
library(kableExtra)
library(xtable)

a1<- matrix(NA, ncol = 3, nrow = 2)
toolmark1.confusion<- data.frame(a1)
colnames(toolmark1.confusion)<- c("Classification", "Match", "Non-Match")
toolmark1.confusion$Classification<- c("Match", "Non-Match")
toolmark1.confusion$Match<- c(41,2)
toolmark1.confusion$`Non-Match`<- c(9,48)

a2<- matrix(NA, ncol = 3, nrow = 2)
toolmark2.confusion<- data.frame(a2)
colnames(toolmark2.confusion)<- c("Classification", "Match", "Non-Match")
toolmark2.confusion$Classification<- c("Match", "Non-Match")
toolmark2.confusion$Match<- c(47,0)
toolmark2.confusion$`Non-Match`<- c(3,50)

chumbley.confusion<-knitr::kable(toolmark1.confusion, digits=0, format = "latex" ,booktabs=TRUE) #%>% kableExtra::kable_styling(latex_options = c("hold"))
hadler.confusion<-knitr::kable(toolmark2.confusion, digits=0, format = "latex" ,booktabs=TRUE) #%>% kableExtra::kable_styling(latex_options = c("hold"))

cat(c("\\begin{table}[!htb]
    \\begin{minipage}{.5\\linewidth}
      \\caption{Chumbley et al. 2010}
      \\centering",
        chumbley.confusion,
    "\\end{minipage}%
    \\begin{minipage}{.5\\linewidth}
      \\centering
        \\caption{Hadler et. al. (2017)}",
       hadler.confusion,
    "\\end{minipage} 
\\end{table}"
))

```
\newpage

>>>>

\section{Introduction}\label{introduction}

@@

\begin{table}[!htb]
    \begin{minipage}{.5\linewidth}
      \caption{Chumbley et al. 2010}
      \centering 
\begin{tabular}{lrr}
\toprule
Classification & Match & Non-Match\\
\midrule
Match & 41 & 9\\
Non-Match & 2 & 48\\
\bottomrule
\end{tabular} \end{minipage}%
    \begin{minipage}{.5\linewidth}
      \centering
        \caption{Hadler et. al. (2017)} 
\begin{tabular}{lrr}
\toprule
Classification & Match & Non-Match\\
\midrule
Match & 47 & 3\\
Non-Match & 0 & 50\\
\bottomrule
\end{tabular} \end{minipage} 
\end{table}\newpage

\bibliographystyle{agsm}
\bibliography{bibliography}

\end{document}
